A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
more about cultural and spatial distance

- Correlation of cultural distances and spatial distance

- Simulation: What is to be expected in case of influence of spatial distance?

>>>>

Table \ref{tab:distanceandcorrelationtable*} shows that the distance networks of *burial type* and *burial construction* are not equivalent. There is also no significant negative correlation. The degree of agreement between two regions in the question of body burial and cremation is therefore not suitable for predicting the similarity of developments in these regions with regard to the dominance of flat or mound graves. Only for the time window at the transition to the Middle Bronze Age from 1800 to 1600calBC is the 5% significance level of the mantle test almost undercut, thus suggesting a statistically significant relationship.

For the relationship between the SED network based on *burial type* and the spatial distance several observations result from Table \ref{tab:distanceandcorrelationtable*}: Surprisingly, cultural distance does not seem to correlate with spatial distance. A significant correlation between the distance measures only reveals itself for the Early Bronze Age time window 2000 to 1800calBC. This means that only in the Early Bronze Age, long before the universal switch to the Urnfield burial, large regions directly adjacent to each other tend to undergo the same developments rather than the ones further away from each other. In the Middle Bronze Age, the SED developments of the *burial type* variable undergo the peaks already observed in Figure \ref{sed_region_matrix}. The correlation between cultural and spatial distance over these peaks is low and even tilts between 1400 and 1200calBC, at the transition to the Late Bronze Age, into the negative -- although not significantly. The cultural distance between several geographically distant regions is then smaller than between several directly adjacent regions. Looking at the SED network on the basis of *burial construction* and examining it for spatial correlation by means of the Table \ref{tab:distanceandcorrelationtable*}, similar conclusions can be drawn as in the *burial type* context. The distance values here are larger overall and the SED differences within the individual spatial distance classes are clearly more accentuated, but here, too, the early bronze age is by far the phase of the largest spatial correlation. This is only significant for the time window between 1800 and 1400calBC. Negative correlation is not indicative for *burial construction*, but here, too, the correlation coefficient approaches zero in the Late Bronze Age.

Simulation: What is to be expected in case of influence of spatial distance?
